Cross-Correlations Between Galaxies and Dispersion-Space Fast Radio Bursts

### 2019-06-12 writeup/dm_space_cross.tex
Work through cross-correlation.

>>>>

One thing that should be true is that the disperion-space distortions
should no effect
on observations that do not use DM information. Lets say we did not bin the
FRBs by dispersion measure but just took the angular cross-power spectrum of the
unbinned FRBs with the galaxies (which may still be binned), $C^{gf}_\ell(\chi)$.
The number of FRBs per unit comoving distance is proportional to
$\chi^2 \bar{n}_{f}(\chi)$, and so
\begin{equation}
    C^{gf}_\ell(\chi) \propto \int \ud\chi' {\chi'}^2 \bar{n}_{f}(\chi')
    C^{gs}_\ell(\chi, \chi').
\end{equation}
Substituting Equation~\ref{e:Clss}, we find that integrating the cross term by
parts gives exact expression required to cancel the $P_{ge}$ part of the local
term and everything is miraculously consistent.
